Model

### 2020-01-20 stats/model.Rmd
push model after test run

model_pred <- read_csv("../saves/model/samples78.csv") %>%
  filter(a == "modelPrediction")%>%
  select(-a)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         id = f,
         item = e,
         age = g, 
         pred = h)

>>>>

model <- read_csv("../webppl/output/samples-reFactor-noRandomEffects_mcmc-2_burn1_lag1_chain1.csv")

model_pred <- model %>%
  filter(a == "modelPrediction")%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)
